Bootstrap Confidence Intervals for Regression Discontinuity Designs

### 2016-02-15 main_paper.tex
References
More references.

The identification of the treatment effect at the treshold is then based on 
comparing treated and untreated units at the cutoff. As a practical matter this 
involves comparing units within a bandwidth just above and just below the 
treshold. That comparison is most commonly done by implementing a local linear
estimator above and below the cutoff within bandwidths chosen to minimize the 
asymptotic mean squared error (AMSE) as proposed by Imbens and Kalyanaraman(2012)
and extensions by Calonico, Cattaneo and Titiunik (2014).

Recently, Calonico, Cattaneo and Titiunik (2014) brought attention to the fact
that the popular implementation of RD designs coupling optimal-AMSE bandwidths
and local polynomial estimation provides confidence intervals (CIs) with
incorrect coverage due to the presence of bias and propose an explicit analytical
bias correction procedure that re-centers and re-scale the CI by estimating a higher 
order approximation of the bias term and adjustment its lenght to account for 
the variation introduced by the bias estimation.

As pointed out by Calonico, Cattaneo and Farrell (2015), ``(...)valid inference
requires the delicate balancing act of selecting a bandwidth small enough
to remove smoothing bias, yet large enough to ensure adequate precision.''
The authors compare the strategies of undersmoothing, and explicit bias 
correction concluding that direct bias-correction with the corresponding 
rescalling of the CI's is a superior approach.

This paper contributes to the bias-corrected RD literature by proposing a simple
bootstrap procedure to correct the first order bias term and directly obtain 
valid CIs that provide the correct coverage. The algorithm proposed is easy to
implement and rely on the same conditions as the explicit bias correction
proposed by Calonico, Cattaneo and Titiunik (2014).

The novel bootstrap procedure is easy to implement and extends to RD designs 
using higher order polynomials, producing valid CIs which are robust to 
bandwidth choice and have similar properties to the analytical procedure in 
Calonico, Cattaneo and Titiunik (2014) while sidestepping the need to derive 
analytical formulas in each case of interest.

@@

Naturally, the estimation of $\tau$ in RD designs focuses on the 
problem of approximating $\mathbbm{E}[Y(1)|X=x]$ and $\mathbbm{E}[Y(0)|X=x]$ 
near the cutoff. Due to its desirable properties when estimating regression 
functions at boundary points, we consider the popular approach of fitting 
separate kernel-weighted local linear regressions in neighborhoods on both 
sides of the threshold.\footnote{See \cite{HTV2001}, \cite{Porter03} or
\cite{FanGijbels92} for discussions of the properties of local polynomial 
regressions for boundary problems.The results presented here are valid for
higher order polynomials and discontinuities at derivatives, like ``Kink RDD''
in Card, Lee and Pei (2009). We focus on the linear case for ease in exposition.}
For the local linear model, we use the following estimator as described in 
\cite{calonico2014},\footnote{Throughout the paper we follow the
notation on \cite{calonico2014} very closely.}
\begin{align*}
 \hat{\tau}(h_{n})&=\hat {\mu}_{+}(h_{n}) -\hat{\mu}_{-}(h_{n})\\
(\hat {\mu}_{+}(h_{n}),\hat {\mu}^{(1)}_{+}(h_{n}))'&= argmin_{b_{0},b_{1}} 
\sum_{i=1}^{N}\mathbbm{1}\{X_{i} \geq 0\}(Y_{i}-b_{0}-X_{i}b_{1})^{2} \cdot K_{h}(X_{i})\\
(\hat {\mu}_{-}(h_{n}),\hat {\mu}^{(1)}_{-}(h_{n}))' &= argmin_{b_{0},b_{1}}
\sum_{i=1}^{N}\mathbbm{1}\{X_{i} < 0\}(Y_{i}-b_{0}-X_{i}b_{1})^{2}\cdot K_{h}(X_{i})
\end{align*}
where $K_{h}(x_{i}) = K\left(\frac{x_{i}}{h}\right)\frac{1}{h}$.

As shown by \cite{HTV2001}, \cite{Porter03} and expanded by \cite{calonico2014} 
identification and inference procedures can be developed based on the following 
assumptions\footnote{The assumptions below are the same as presented by \cite{calonico2014}.}
\begin{assumption}\label{A1}
 For some $\kappa_{0} > 0$, the following holds in the neighborhood 
 $(-\kappa_{0},\kappa_{0})$ around the cutoff $ \bar{x}= 0$:
 \begin{enumerate}
  \item $E[\left.Y_{i}^{4}\right|X_{i}=x]$ is bounded and the density of $X$, 
  $f(x)$, is continuous and bounded away from zero.
  \item $\mu_{+}(x)=\mathbbm{E}[\left.Y_{i}(1)\right|X_{i}=x]$ and $\mu_{-}(x)=
  \mathbbm{E}[\left.Y_{i}(0)\right|X_{i}=x]$ are $S$ times continuously 
  differentiable.
  \item $\sigma^{2}_{+}(x)=\mathbbm{V}[\left.Y_{i}(1)\right|X_{i}=x]$ and 
  $\sigma^{2}_{-}(x)=\mathbbm{V}[\left.Y_{i}(0)\right|X_{i}=x]$ are continuous 
  and bounded away from zero.
 \end{enumerate}
\end{assumption}

The conditions in Assumption \ref{A1} are the usual smoothness and existence 
conditions in which the RD literature relies. Its second part is important for 
the characterization of the leading bias term that will be the focus of the bias
correction procedures described in \cite{calonico2014} and in the novel
 bootstrap procedure proposed in Section \ref{boot}.

@@

\cite{calonico2014} point out that the conventional approaches to construct 
confidence intervals for $\tau$ using the local linear estimator rely on a 
large-sample approximation for the standardized $t$-statistic that is valid only
if the bandwidth shrink fast enough to eliminate the leading bias term 
contribution to the approximation. Hence, if $nh_{n}^{5}\rightarrow0$ and 
$nh_{n}\rightarrow \infty$, then
 \begin{align}
  T(h_{n})=\frac{\hat{\tau}(h_{n})-\tau}{\sqrt{V(h_{n})}}\rightarrow_{d}N(0,1),
  \text{        }V(h_{n})=\mathbbm{V}[\left.\tau(h_{n})\right|\chi_{n}],
  \text{        }\chi_{n}=[X_{1}, \dots X_{n}]^{\prime}
 \end{align}
 The conditional variance $V(h_{n})$ depends on the $\sigma^{2}_{+}=
 lim_{x \rightarrow 0^{+}}\sigma^{2}_{+}(x)$ and $\sigma^{2}_{-}=
 lim_{x \rightarrow 0^{-}}\sigma^{2}_{-}(x)$ as well as $h_{n}$ and known 
 quantities that depend on the kernel and order of polynomial used in the 
 estimation. Under these conditions we could use a conventional confidence 
 interval for $\tau$ given by
 \begin{align}
  I(h_{n})=\left[\hat{\tau}(h_{n})\pm \Phi^{-1}_{1-\frac{\alpha}{2}}\sqrt{V(h_{n})} \right]
 \end{align}
with $\Phi^{-1}_{1-\frac{\alpha}{2}}$ being the $\alpha$-quantile of the 
standard normal distribution. However, most approaches to select the bandwidth, 
$h_{n}$ in the literature, including the widely used optimal-AMSE bandwidth 
selector proposed by \cite{IK} lead to bandwidth choices that are ``too large'' 
since they do not satisfy the condition $nh_{n}^{5}\rightarrow0$, leading to a 
first-order bias in the distributional approximation used to construct the 
confidence intervals.

\cite{calonico2014} resolve the problem by deriving the analytical form of the 
first-order bias and correcting it directly. To obtain correct coverage the 
confidence interval needs not only to be recentered to correct the bias, but 
also rescaled to allow for the additional variability introduced by the bias 
correction. Their approach rely on obtaining a bias-corrected  estimator, 
$\hat{\tau}^{bc}$ and its adjusted variance. It is important first to note that 
the first-order bias term itself will depend on the bandwidth $h_{n}$. The 
approximate bias term can be described as:
\begin{align*}
     E[\hat{\tau}(h_{n})|\chi_{n}]-\tau=& h_{n}^{2}\mathsf{B}(h_{n})\{1+o_{p}(1)\}\\
     \mathsf{B}(h_{n})=&\frac{\mu_{+}^{(2)}}{2!}\mathfrak{B}_{+}(h_{n})-\frac{\mu_{-}^{(2)}}{2!}\mathfrak{B}_{-}(h_{n})
   \end{align*}
where $\mathfrak{B}_{+}(h_{n})$ and $\mathfrak{B}_{-}(h_{n})$ are observed 
quantities that depend on the data, kernel and $h_{n}$. The plug-in 
bias-corrected estimator then requires estimates for the second derivatives of 
the conditional mean from above and below the cutoff, $\mu_{+}^{(2)}$ and 
$\mu_{-}^{(2)}$. \cite{calonico2014} propose using a conventional local quadratic
estimator, i.e. one order higher than the polynomial used to obtain $\hat{\tau}$,
using a (potentially) different pilot bandwidth $b_{n}$.
\begin{align*}
     \hat{\tau}^{bc}(h_{n}, b_{n})=& \hat{\tau}-h_{n}^{2}\hat{\mathsf{B}}(h_{n},b_{n})\\
     \hat{\mathsf{B}}(h_{n})=&\frac{\hat{\mu}_{+}^{(2)}(b_{n})}{2!}
     \mathfrak{B}_{+}(h_{n})-\frac{\hat{\mu}_{-}^{(2)}(b_{n})}{2!}\mathfrak{B}_{-}(h_{n})
   \end{align*}
By incorporating the contribution of both $\hat{\tau}(h_{n})$ and 
$\hat{\mathsf{B}}(h_{n},b_{n})$ to the asymptotic distribution of the estimator,
\cite{calonico2014} obtain a robust confidence interval with a different 
asymptotic variance in general. So under Assumptions\ref{A1} and \ref{A2}, if 
$n\min\{h_{n}^{5}, b_{n}^{5}\}max\{h_{n}^{2}, b_{n}^{2}\}\rightarrow 0$ and 
$n\min\{h_{n}, b_{n}\}\rightarrow \infty$ and $\kappa \max\{h_{n},b_{n}\}< 
\kappa_{0}$, they show that
\begin{align}
  T^{rbc}(h_{n}, b_{n})=\frac{\hat{\tau}^{bc}(h_{n}, b_{n})-\tau}{\sqrt{V^{bc}(h_{n}, b_{n})}}\rightarrow_{d}N(0,1),
  \text{        }V^{bc}(h_{n}, b_{n})=V(h_{n})+C^{bc}(h_{n}, b_{n})\\
 \end{align}
where the additional term $C^{bc}(h_{n}, b_{n})$ depends on the (asymptotic) 
variability of the bias estimate used for correction as well as its correlation 
with the original RD estimator $\hat{\tau}(h_{n})$.\footnote{The details of the 
formulas are currently ommitted from this paper since their form is not relevant
to the bootstrap procedure innovation proposed. The details can be found at 
\cite{calonico2014} Appendix}  Under these conditions we can construct a valid 
confidence interval for $\tau$ given by
 \begin{align}
  I^{rbc}(h_{n}, b_{n})=\left[\left(\hat{\tau}(h_{n})-h_{n}^{2}\hat{\mathsf{B}}
  (h_{n},b_{n})\right)\pm \Phi^{-1}_{1-\frac{\alpha}{2}}\sqrt{V(h_{n})+C^{bc}
  (h_{n}, b_{n})} \right]
 \end{align}

This approach is shown by the authors to significantly coverage of the CIs 
constructed and provides practitioners with a new toolset to perform inference 
that is more robust to the choice of bandwidth. We build upon the insight 
provided by \cite{calonico2014} bias-corrected estimator and propose a simple 
bootstrap procedure that can directly construct the robust CIs without requiring
the derivation of analytical formulas and direct estimators for the bias, 
variance and covariance terms, while relying on the same first-order bias 
correction approximation proposed by that paper.

@@

\section{Simulation Evidence}\label{sim}
This section presents evidence from Monte Carlo simulations that the bootstrap bias correction procedures proposed in Section \ref{boot} produces valid, robust confidence intervals similar to the ones obtained by the analytical procedures established in \cite{calonico2014}. The bootstrap CIs obtained compare favourably to the analytical alternative, with coverage closer to the nominal size of the desired test and shorter lenght of the intervals in the specifications implemented.

We selected three data generating processes (DGP) that are widely used in the RD literature to evaluate the performance of the proposed bootstrap procedure, those are the same chosen by \cite{calonico2014} and \cite{IK} and provide a good testing ground for bias correction due to their exacerbated curvature. To be specific, the pseudo data are generated as 500 i.i.d. draws from:
\begin{align*}
& Y_{i} = \mu_{j}(X_{i}) + \epsilon_{i}, \;\;\; X_{i} \sim  (2 B (2,4) - 1)), \\
& \epsilon_{i} \sim N(0, \sigma^{2}), \;\;\; \sigma = 0.1295, \;\;\; j = 1,2,3.
\end{align*}
Three different choices of functional forms for $\mu_{j}(x)$ are as follows:
\begin{align}
\mu_{1}(x) & = 
\begin{cases}
0.48 + 1.27x + 7.18x^{2} + 20.21x^{3} + 21.54x^{4} + 7.33x^{5}, \;\;\;\; & \text{if} \;\; x < 0, \\
0.52 + 0.84x - 3.00x^{2} + 7.99x^3 - 9.01x^4 + 3.56x^{5},  & \text{if} \;\; x \ge 0.
\end{cases}
\\
\mu_{2}(x) & = 
\begin{cases}
3.71 + 2.30x + 3.28x^2 + 1.45x^3 + 0.23x^4 + 0.03x^5, \;\; & \text{if} \;\; x < 0, \\
0.26 + 18.49x - 54.81x^2 + 74.30x^3 - 45.02x^4 + 9.83x^5,  & \text{if} \;\; x \ge 0.
\end{cases}
\\
\mu_{3}(x) & =
\begin{cases}
0.48 + 1.27x + 0.5 \times 7.18x^{2}+ \\
+ 0.7 \times 20.21x^3 + 1.1 \times 21.54x^4 + 1.5 \times 7.33x^5, \;\;\;\;\;\;\;\;\;\;\;\; & \text{if} \;\; x < 0, \\
0.52 + 0.84x - 0.1 \times 3.00x^{2}+ \\
+ 0.3 \times 7.99x^3 - 0.1 \times 9.01x^4 + 3.56x^5, & \text{if} \;\; x \ge 0.
\end{cases}
\end{align}

The functional form for $\mu_{1}(x)$ and $\mu_{2}(x)$ follow the data observed by Lee (2008) and Ludwig and Miller (2007), respectively, while $\mu_{3}(x)$ is a transformation of $\mu_{1}(x)$ designed to emphasize its curvature and therefore bias in the usual RD approach. For the simulation studies, we used 250 bootstraps for bias correction, 999 bootstraps to calculate confidence interval and a total 500 replications. All results presented are based on a 0.95 desired confidence level. Table \ref{Tb1} presents the main results in which a local-linear RD estimator ($p=1$) is employed with the bias-correction based on a local-quadratic approximation ($q=2$). Table \ref{Tb2} presents similar results for $p=2$ and $q=3$.

\begin{table}[ht] \label{Tb1}
	\caption{Summary of estimates ($p = 1, q = 2$)}
	\centering
	\begin{tabular}{ccccccc}
		\hline
		DGP & True & Bias & SD & MSE & CI coverage & CI length \\ 
		\hline
		\multicolumn{7}{c}{Panel A: Bootstrap Bias-Correction} \\
		1 & 0.04 & -0.013 & 0.067 & 0.068 & 0.938 & 0.243 \\ 
		2 & -3.45 & -0.014 & 0.083 & 0.084 & 0.954 & 0.319 \\ 
		3 & 0.04 & -0.006 & 0.069 & 0.070 & 0.956 & 0.247 \\ 
		&&&&&& \\
		\multicolumn{7}{c}{Panel B: Analytical Bias Correction (CCT 2014)} \\
		1 & 0.04 & -0.016 & 0.068 & 0.070 & 0.908 & 0.244 \\ 
		2 & -3.45 & -0.014 & 0.092 & 0.093 & 0.928 & 0.350 \\ 
		3 & 0.04 & -0.004 & 0.071 & 0.071 & 0.918 & 0.249 \\ 
		\hline
	\end{tabular}
\end{table}

\begin{table}[ht]\label{Tb2}
	\caption{Summary of estimates from bootstrap ($p = 2, q = 3$)}
	\centering
	\begin{tabular}{ccccccc}
		\hline
		DGP & True & Bias & SD & MSE & CI coverage & CI length \\ 
		\hline
		\multicolumn{7}{c}{Panel A: Uniform Kernel} \\
		1 & 0.04 & -0.002 & 0.075 & 0.075 & 0.958 & 0.295 \\ 
		2 & -3.45 & 0.002 & 0.087 & 0.086 & 0.934 & 0.302 \\ 
		3 & 0.04 & -0.008 & 0.083 & 0.083 & 0.942 & 0.292 \\ 
		&&&&&& \\
		\multicolumn{7}{c}{Panel B: Analytical Bias Correction (CCT 2014)} \\
		1 & 0.04 & -0.004 & 0.082 & 0.082 & 0.926 & 0.295 \\ 		
		2 & -3.45 & -0.005 & 0.078 & 0.078 & 0.960 & 0.323 \\ 		
		3 & 0.04 & -0.003 & 0.080 & 0.080 & 0.938 & 0.295 \\ 
		\hline
	\end{tabular}
\end{table}

@@

>>>>

The identification of the treatment effect at the treshold is then based on 
comparing treated and untreated units at the cutoff. As a practical matter this 
involves comparing units within a bandwidth just above and just below the 
treshold. That comparison is most commonly done by implementing a local linear
estimator above and below the cutoff within bandwidths chosen to minimize the 
asymptotic mean squared error (AMSE) as proposed by Imbens and Kalyanaraman(2012)
and extensions by \cite{calonico2014} (CCT, henceforth).

Recently, CCT brought attention to the fact that the popular implementation of RD designs coupling optimal-AMSE bandwidths
and local polynomial estimation provides confidence intervals (CIs) with
incorrect coverage due to the presence of bias and propose an explicit analytical
bias correction procedure that re-centers and re-scale the CI by estimating a higher 
order approximation of the bias term and adjustment its lenght to account for 
the variation introduced by the bias estimation.

As pointed out by \cite{ccf2016}, ``(...)valid inference
requires the delicate balancing act of selecting a bandwidth small enough
to remove smoothing bias, yet large enough to ensure adequate precision.''
The authors compare the strategies of undersmoothing, and explicit bias 
correction concluding that direct bias-correction with the corresponding 
rescalling of the CI's is a superior approach.

This paper contributes to the bias-corrected RD literature by proposing a simple
bootstrap procedure to correct the first order bias term and directly obtain 
valid CIs that provide the correct coverage. The algorithm proposed is easy to
implement and rely on the same conditions as the explicit bias correction
proposed by CCT.

The novel bootstrap procedure is easy to implement and extends to RD designs 
using higher order polynomials, producing valid CIs which are robust to 
bandwidth choice and have similar properties to the analytical procedure in 
CCT while sidestepping the need to derive analytical formulas in each case of interest.

@@

Naturally, the estimation of $\tau$ in RD designs focuses on the 
problem of approximating $\mathbbm{E}[Y(1)|X=x]$ and $\mathbbm{E}[Y(0)|X=x]$ 
near the cutoff. Due to its desirable properties when estimating regression 
functions at boundary points, we consider the popular approach of fitting 
separate kernel-weighted local linear regressions in neighborhoods on both 
sides of the threshold.\footnote{See \cite{HTV2001}, \cite{Porter03} or
\cite{FanGijbels92} for discussions of the properties of local polynomial 
regressions for boundary problems.The results presented here are valid for
higher order polynomials and discontinuities at derivatives, like ``Kink RDD.'' We focus on the linear case for ease in exposition.}
For the local linear model, we use the following estimator as described in 
CCT,\footnote{Throughout the paper we follow the notation on \cite{calonico2014} very closely.}
\begin{align*}
 \hat{\tau}(h_{n})&=\hat {\mu}_{+}(h_{n}) -\hat{\mu}_{-}(h_{n})\\
(\hat {\mu}_{+}(h_{n}),\hat {\mu}^{(1)}_{+}(h_{n}))'&= argmin_{b_{0},b_{1}} 
\sum_{i=1}^{N}\mathbbm{1}\{X_{i} \geq 0\}(Y_{i}-b_{0}-X_{i}b_{1})^{2} \cdot K_{h}(X_{i})\\
(\hat {\mu}_{-}(h_{n}),\hat {\mu}^{(1)}_{-}(h_{n}))' &= argmin_{b_{0},b_{1}}
\sum_{i=1}^{N}\mathbbm{1}\{X_{i} < 0\}(Y_{i}-b_{0}-X_{i}b_{1})^{2}\cdot K_{h}(X_{i})
\end{align*}
where $K_{h}(x_{i}) = K\left(\frac{x_{i}}{h}\right)\frac{1}{h}$.

As shown by \cite{HTV2001}, \cite{Porter03} and expanded by CCT 
identification and inference procedures can be developed based on the following 
assumptions\footnote{The assumptions below are the same as presented by CCT.}
\begin{assumption}\label{A1}
 For some $\kappa_{0} > 0$, the following holds in the neighborhood 
 $(-\kappa_{0},\kappa_{0})$ around the cutoff $ \bar{x}= 0$:
 \begin{enumerate}
  \item $E[\left.Y_{i}^{4}\right|X_{i}=x]$ is bounded and the density of $X$, 
  $f(x)$, is continuous and bounded away from zero.
  \item $\mu_{+}(x)=\mathbbm{E}[\left.Y_{i}(1)\right|X_{i}=x]$ and $\mu_{-}(x)=
  \mathbbm{E}[\left.Y_{i}(0)\right|X_{i}=x]$ are $S$ times continuously 
  differentiable.
  \item $\sigma^{2}_{+}(x)=\mathbbm{V}[\left.Y_{i}(1)\right|X_{i}=x]$ and 
  $\sigma^{2}_{-}(x)=\mathbbm{V}[\left.Y_{i}(0)\right|X_{i}=x]$ are continuous 
  and bounded away from zero.
 \end{enumerate}
\end{assumption}

The conditions in Assumption \ref{A1} are the usual smoothness and existence 
conditions in which the RD literature relies. Its second part is important for 
the characterization of the leading bias term that will be the focus of the bias
correction procedures described in CCT and in the novel
 bootstrap procedure proposed in Section \ref{boot}.

@@

CCT point out that the conventional approaches to construct 
confidence intervals for $\tau$ using the local linear estimator rely on a 
large-sample approximation for the standardized $t$-statistic that is valid only
if the bandwidth shrink fast enough to eliminate the leading bias term 
contribution to the approximation. Hence, if $nh_{n}^{5}\rightarrow0$ and 
$nh_{n}\rightarrow \infty$, then
 \begin{align}
  T(h_{n})=\frac{\hat{\tau}(h_{n})-\tau}{\sqrt{V(h_{n})}}\rightarrow_{d}N(0,1),
  \text{        }V(h_{n})=\mathbbm{V}[\left.\tau(h_{n})\right|\chi_{n}],
  \text{        }\chi_{n}=[X_{1}, \dots X_{n}]^{\prime}
 \end{align}
 The conditional variance $V(h_{n})$ depends on the $\sigma^{2}_{+}=
 lim_{x \rightarrow 0^{+}}\sigma^{2}_{+}(x)$ and $\sigma^{2}_{-}=
 lim_{x \rightarrow 0^{-}}\sigma^{2}_{-}(x)$ as well as $h_{n}$ and known 
 quantities that depend on the kernel and order of polynomial used in the 
 estimation. Under these conditions we could use a conventional confidence 
 interval for $\tau$ given by
 \begin{align}
  I(h_{n})=\left[\hat{\tau}(h_{n})\pm \Phi^{-1}_{1-\frac{\alpha}{2}}\sqrt{V(h_{n})} \right]
 \end{align}
with $\Phi^{-1}_{1-\frac{\alpha}{2}}$ being the $\alpha$-quantile of the 
standard normal distribution. However, most approaches to select the bandwidth, 
$h_{n}$ in the literature, including the widely used optimal-AMSE bandwidth 
selector proposed by \cite{IK} lead to bandwidth choices that are ``too large'' 
since they do not satisfy the condition $nh_{n}^{5}\rightarrow0$, leading to a 
first-order bias in the distributional approximation used to construct the 
confidence intervals.

CCT resolve the problem by deriving the analytical form of the 
first-order bias and correcting it directly. To obtain correct coverage the 
confidence interval needs not only to be recentered to correct the bias, but 
also rescaled to allow for the additional variability introduced by the bias 
correction. Their approach rely on obtaining a bias-corrected  estimator, 
$\hat{\tau}^{bc}$ and its adjusted variance. It is important first to note that 
the first-order bias term itself will depend on the bandwidth $h_{n}$. The 
approximate bias term can be described as:
\begin{align*}
     E[\hat{\tau}(h_{n})|\chi_{n}]-\tau=& h_{n}^{2}\mathsf{B}(h_{n})\{1+o_{p}(1)\}\\
     \mathsf{B}(h_{n})=&\frac{\mu_{+}^{(2)}}{2!}\mathfrak{B}_{+}(h_{n})-\frac{\mu_{-}^{(2)}}{2!}\mathfrak{B}_{-}(h_{n})
   \end{align*}
where $\mathfrak{B}_{+}(h_{n})$ and $\mathfrak{B}_{-}(h_{n})$ are observed 
quantities that depend on the data, kernel and $h_{n}$. The plug-in 
bias-corrected estimator then requires estimates for the second derivatives of 
the conditional mean from above and below the cutoff, $\mu_{+}^{(2)}$ and 
$\mu_{-}^{(2)}$. CCT propose using a conventional local quadratic
estimator, i.e. one order higher than the polynomial used to obtain $\hat{\tau}$,
using a (potentially) different pilot bandwidth $b_{n}$.
\begin{align*}
     \hat{\tau}^{bc}(h_{n}, b_{n})=& \hat{\tau}-h_{n}^{2}\hat{\mathsf{B}}(h_{n},b_{n})\\
     \hat{\mathsf{B}}(h_{n})=&\frac{\hat{\mu}_{+}^{(2)}(b_{n})}{2!}
     \mathfrak{B}_{+}(h_{n})-\frac{\hat{\mu}_{-}^{(2)}(b_{n})}{2!}\mathfrak{B}_{-}(h_{n})
   \end{align*}
By incorporating the contribution of both $\hat{\tau}(h_{n})$ and 
$\hat{\mathsf{B}}(h_{n},b_{n})$ to the asymptotic distribution of the estimator,
\cite{calonico2014} obtain a robust confidence interval with a different 
asymptotic variance in general. So under Assumptions\ref{A1} and \ref{A2}, if 
$n\min\{h_{n}^{5}, b_{n}^{5}\}max\{h_{n}^{2}, b_{n}^{2}\}\rightarrow 0$ and 
$n\min\{h_{n}, b_{n}\}\rightarrow \infty$ and $\kappa \max\{h_{n},b_{n}\}< 
\kappa_{0}$, they show that
\begin{align}
  T^{rbc}(h_{n}, b_{n})=\frac{\hat{\tau}^{bc}(h_{n}, b_{n})-\tau}{\sqrt{V^{bc}(h_{n}, b_{n})}}\rightarrow_{d}N(0,1),
  \text{        }V^{bc}(h_{n}, b_{n})=V(h_{n})+C^{bc}(h_{n}, b_{n})\\
 \end{align}
where the additional term $C^{bc}(h_{n}, b_{n})$ depends on the (asymptotic) 
variability of the bias estimate used for correction as well as its correlation 
with the original RD estimator $\hat{\tau}(h_{n})$.\footnote{The details of the 
formulas are currently ommitted from this paper since their form is not relevant
to the bootstrap procedure innovation proposed. The details can be found at 
CCT Appendix}  Under these conditions we can construct a valid 
confidence interval for $\tau$ given by
 \begin{align}
  I^{rbc}(h_{n}, b_{n})=\left[\left(\hat{\tau}(h_{n})-h_{n}^{2}\hat{\mathsf{B}}
  (h_{n},b_{n})\right)\pm \Phi^{-1}_{1-\frac{\alpha}{2}}\sqrt{V(h_{n})+C^{bc}
  (h_{n}, b_{n})} \right]
 \end{align}

This approach is shown by the authors to significantly coverage of the CIs 
constructed and provides practitioners with a new toolset to perform inference 
that is more robust to the choice of bandwidth. We build upon the insight 
provided by CCT bias-corrected estimator and propose a simple 
bootstrap procedure that can directly construct the robust CIs without requiring
the derivation of analytical formulas and direct estimators for the bias, 
variance and covariance terms, while relying on the same first-order bias 
correction approximation proposed by that paper.

@@

\section{Simulation Evidence}\label{sim}
This section presents evidence from Monte Carlo simulations that the bootstrap 
bias correction procedures proposed in Section \ref{boot} produces valid, robust
confidence intervals similar to the ones obtained by the analytical procedures 
established in CCT. The bootstrap CIs obtained compare favourably
to the analytical alternative, with coverage closer to the nominal size of the 
desired test and shorter lenght of the intervals in the specifications implemented.

We selected three data generating processes (DGP) that are widely used in the RD
literature to evaluate the performance of the proposed bootstrap procedure, 
those are the same chosen by CCT and \cite{IK} and provide a 
good testing ground for bias correction due to their exacerbated curvature. 
To be specific, the pseudo data are generated as 500 i.i.d. draws from:
\begin{align*}
& Y_{i} = \mu_{j}(X_{i}) + \epsilon_{i}, \;\;\; X_{i} \sim  (2 B (2,4) - 1)), \\
& \epsilon_{i} \sim N(0, \sigma^{2}), \;\;\; \sigma = 0.1295, \;\;\; j = 1,2,3.
\end{align*}
Three different choices of functional forms for $\mu_{j}(x)$ are as follows:
\begin{align}
\mu_{1}(x) & = 
\begin{cases}
0.48 + 1.27x + 7.18x^{2} + 20.21x^{3} + 21.54x^{4} + 7.33x^{5}, \;\;\;\; & \text{if} \;\; x < 0, \\
0.52 + 0.84x - 3.00x^{2} + 7.99x^3 - 9.01x^4 + 3.56x^{5},  & \text{if} \;\; x \ge 0.
\end{cases}
\\
\mu_{2}(x) & = 
\begin{cases}
3.71 + 2.30x + 3.28x^2 + 1.45x^3 + 0.23x^4 + 0.03x^5, \;\; & \text{if} \;\; x < 0, \\
0.26 + 18.49x - 54.81x^2 + 74.30x^3 - 45.02x^4 + 9.83x^5,  & \text{if} \;\; x \ge 0.
\end{cases}
\\
\mu_{3}(x) & =
\begin{cases}
0.48 + 1.27x + 0.5 \times 7.18x^{2}+ \\
+ 0.7 \times 20.21x^3 + 1.1 \times 21.54x^4 + 1.5 \times 7.33x^5, \;\;\;\;\;\;\;\;\;\;\;\; & \text{if} \;\; x < 0, \\
0.52 + 0.84x - 0.1 \times 3.00x^{2}+ \\
+ 0.3 \times 7.99x^3 - 0.1 \times 9.01x^4 + 3.56x^5, & \text{if} \;\; x \ge 0.
\end{cases}
\end{align}

The functional form for $\mu_{1}(x)$ and $\mu_{2}(x)$ follow the data observed 
by by\cite{lee2008} and \cite{ludwig2007}, respectively, while $\mu_{3}(x)$ is
a transformation of $\mu_{1}(x)$ designed to emphasize its curvature and 
therefore bias in the usual RD approach. For the simulation studies, we used 
250 bootstraps for bias correction, 999 bootstraps to calculate confidence 
interval and a total 500 replications. All results presented are based on a 
0.95 desired confidence level. Table \ref{Tb1} presents the main results in which
a local-linear RD estimator ($p=1$) is employed with the bias-correction based 
on a local-quadratic approximation ($q=2$). Table \ref{Tb2} presents similar 
results for $p=2$ and $q=3$.

\begin{table}[ht] \label{Tb1}
	\caption{Summary of Results ($p = 1, q = 2$)}
	\centering
	\begin{tabular}{ccccccc}
		\hline
		DGP & True & Bias & SD & MSE & CI coverage & CI length \\ 
		\hline
		\multicolumn{7}{c}{Panel A: Bootstrap Bias-Correction} \\
		1 & 0.04 & -0.013 & 0.067 & 0.068 & 0.938 & 0.243 \\ 
		2 & -3.45 & -0.014 & 0.083 & 0.084 & 0.954 & 0.319 \\ 
		3 & 0.04 & -0.006 & 0.069 & 0.070 & 0.956 & 0.247 \\ 
		&&&&&& \\
		\multicolumn{7}{c}{Panel B: Analytical Bias Correction (CCT 2014)} \\
		1 & 0.04 & -0.016 & 0.068 & 0.070 & 0.908 & 0.244 \\ 
		2 & -3.45 & -0.014 & 0.092 & 0.093 & 0.928 & 0.350 \\ 
		3 & 0.04 & -0.004 & 0.071 & 0.071 & 0.918 & 0.249 \\ 
		\hline
	\end{tabular}
\end{table}

\begin{table}[ht]\label{Tb2}
	\caption{Summary of Results ($p = 2, q = 3$)}
	\centering
	\begin{tabular}{ccccccc}
		\hline
		DGP & True & Bias & SD & MSE & CI coverage & CI length \\ 
		\hline
		\multicolumn{7}{c}{Panel A: Uniform Kernel} \\
		1 & 0.04 & -0.002 & 0.075 & 0.075 & 0.958 & 0.295 \\ 
		2 & -3.45 & 0.002 & 0.087 & 0.086 & 0.934 & 0.302 \\ 
		3 & 0.04 & -0.008 & 0.083 & 0.083 & 0.942 & 0.292 \\ 
		&&&&&& \\
		\multicolumn{7}{c}{Panel B: Analytical Bias Correction (CCT 2014)} \\
		1 & 0.04 & -0.004 & 0.082 & 0.082 & 0.926 & 0.295 \\ 		
		2 & -3.45 & -0.005 & 0.078 & 0.078 & 0.960 & 0.323 \\ 		
		3 & 0.04 & -0.003 & 0.080 & 0.080 & 0.938 & 0.295 \\ 
		\hline
	\end{tabular}
\end{table}

As can be seen on the tables above, the bootstrap bias-correction procedure
proposed in this paper provides a simple alternative to obtain valid robust
confidence intervals in RD designs and performs well compared to the analytical 
bias correction procedures proposed by CCT.

@@

%%%%%REFERENCES%%%%%%%%%
\clearpage
\bibliographystyle{jpe}
\bibliography{bootrd}
